Word learning at the semantics pragmatics interface

### 2020-04-03 paper/supplementary_material.Rmd
clean repo

We modeled the trial by trial data in the following way: `correct ~ age * alignment + (alignment | subid) + (age * alignment | item) + (age * alignment | agent)`. We pre-registered to include item as a fixed effect in Experiment 3. The corresponding model was too complex to be constrained by the data. Furthermore, as explained in Experiment 1, items were chosen based on their rated age of acquisition. That is, we assumed that they are not necessarily different kinds but that they represent different locations on a distribution of required semantic knowledge. For further model specifications see [Experiment 1](#experiment-1-mutual-exclusivity)).

@@

The experiments reported above show that children are sensitive to the types of information sources we intended to manipulate. Experiment 1 showed that children of all age groups are make a mutual exclusivity inference, that the strength of this inference increases with age and, crucially, that it depends on the type of familiar object that is presented. Experiment 2 showed that three- and four-year-olds are sensitive the common ground manipulation we implemented and that this inference increases with age. Finally, experiment 3 showed that children respond differently depending on how the mutual exclusivity inference and the common ground inference are aligned with one another. In the next section, we use Bayesian cognitive models to address the question of *how* information sources are integrated when the two inferences are combined with one another.

@@

```{r fig5, include = T, fig.align = "center", fig.cap = "Predicting information integration across development. Model predictions based on the integration model. Colored lines show developmental trajectories for each familiar object and condition based on 300 random draws from the model posterior distribution. Top row (blue) shows the congruent condition and the bottom row (red) shows the inconguent condition. Familiar objects are ordered based on their rated age of acquisition (left o right). Dashed black lines show smoothed conditional mean of the data with 95\\% CI (in grey). Light dots are individual data points.", fig.width=12, fig.height = 4}
# comb_data_binned <- comb_data%>%
#   group_by(subage, alignment, item)%>%
#   summarize(k = sum(correct), n = n())%>%
#   ungroup() %>%
#   mutate(a = 1 + k,
#          b = 1 + n - k,
#          data_mean = (a-1)/(a+b-2),
#          data_ci_lower  = qbeta(.025, a, b),
#          data_ci_upper = qbeta(.975, a, b),
#          age = factor(subage))%>%
#   select(-a,-b,-n,-k)%>%
#   left_join(aoa_ratings) %>%
#   ungroup()%>%
#   mutate(item = fct_reorder(factor(item), mean_aoa))
# 
# select_pred <- sample(1:20000, 60)
# 
# plot_prag_pred <- readRDS("../saves/model_pred_prag.rds")%>%
#   filter(iteration %in% select_pred)%>%
#   left_join(aoa_ratings) %>%
#   ungroup()%>%
#   mutate(item = fct_reorder(factor(item), mean_aoa))
# 
# 
#  saveRDS(plot_prag_pred, "../saves/plot_prag_pred.rds")

@@

```{r table5}
model_comp_pred <- readRDS("../saves/pred_model_comparison.rds")%>%
  mutate(model = factor(model),
         `Model comparison` = fct_recode(model, 
                            "integration vs no word knowledge" = "prag_vs_global",
                            "integration vs no common ground" = "prag_vs_flat",
                            "integration vs no mutual exclusivity" = "prag_vs_prior",
                            "no word knowledge vs no mutual exclusivity" = "global_vs_flat",
                            "no word knowledge vs no common ground" = "global_vs_prior",
                            "no mutual exclusivity vs no common ground" = "flat_vs_prior"),
        `Bayes factor` = format(round(exp(logBF),2), trim = T, justify = "right", digits = 2))%>%
  select(-logBF, -model)

>>>>

We modeled the trial by trial data in the following way: `correct ~ age * alignment + (alignment | subid) + (age * alignment | object) + (age * alignment | agent)`. We pre-registered to include item as a fixed effect in Experiment 3. The corresponding model was too complex to be constrained by the data. Furthermore, as explained in Experiment 1, items were chosen based on their rated age of acquisition. That is, we assumed that they are not necessarily different kinds but that they represent different locations on a distribution of required semantic knowledge. For further model specifications see [Experiment 1](#experiment-1-mutual-exclusivity)).

@@

The experiments reported above show that children are sensitive to the types of information sources we intended to manipulate. Experiment 1 showed that children of all age groups make a mutual exclusivity inference, that the strength of this inference increases with age and, crucially, that it depends on the type of familiar object that is presented. Experiment 2 showed that children are sensitive the common ground manipulation we implemented and that this inference increases with age. Finally, experiment 3 showed that children respond differently depending on how the mutual exclusivity inference and the common ground inference are aligned with one another. In the next section, we use Bayesian cognitive models to address the question of *how* information sources are integrated when inferences are combined with one another.

@@

```{r fig5, include = T, fig.align = "center", fig.cap = "Predicting information integration across development. Model predictions based on the integration model. Colored lines show developmental trajectories for each familiar object and condition based on 300 random draws from the model posterior distribution. Top row (blue) shows the congruent condition and the bottom row (red) shows the inconguent condition. Familiar objects are ordered based on their rated age of acquisition (left to right). Dashed black lines show smoothed conditional mean of the data with 95\\% CI (in grey). Light dots are individual data points.", fig.width=12, fig.height = 4}
# comb_data_binned <- comb_data%>%
#   group_by(subage, alignment, item)%>%
#   summarize(k = sum(correct), n = n())%>%
#   ungroup() %>%
#   mutate(a = 1 + k,
#          b = 1 + n - k,
#          data_mean = (a-1)/(a+b-2),
#          data_ci_lower  = qbeta(.025, a, b),
#          data_ci_upper = qbeta(.975, a, b),
#          age = factor(subage))%>%
#   select(-a,-b,-n,-k)%>%
#   left_join(aoa_ratings) %>%
#   ungroup()%>%
#   mutate(item = fct_reorder(factor(item), mean_aoa))
# 
# select_pred <- sample(1:20000, 60)
# 
# plot_prag_pred <- readRDS("../saves/model_pred_prag.rds")%>%
#   filter(iteration %in% select_pred)%>%
#   left_join(aoa_ratings) %>%
#   ungroup()%>%
#   mutate(item = fct_reorder(factor(item), mean_aoa))
# 
# 
#  saveRDS(plot_prag_pred, "../saves/plot_prag_pred.rds")

@@

```{r table5}
model_comp_pred <- readRDS("../saves/pred_model_comparison.rds")%>%
  mutate(model = factor(model),
         `Model comparison` = fct_recode(model, 
                            "integration vs no word knowledge" = "prag_vs_global",
                            "integration vs no common ground" = "prag_vs_flat",
                            "integration vs no mutual exclusivity" = "prag_vs_prior",
                            "no word knowledge vs no mutual exclusivity" = "global_vs_flat",
                            "no word knowledge vs no common ground" = "global_vs_prior",
                            "no mutual exclusivity vs no common ground" = "flat_vs_prior"),
        `Bayes factor` = format(round(exp(logBF)), trim = T, justify = "right", scientific = F))%>%
  select(-logBF, -model)
